\documentclass[a4paper,12pt]{article}
\usepackage{array}
\begin{document}
\title{Minutes of Meeting for Internal Meeting \#4}
\maketitle
\begin{tabular}{>{\bfseries}l l}	
Project name&Formal and secure messaging on a mobile platform\\
Calling by&Group 15\\
Time and date&2012-09-18 08:15-09:30\\
Place&R30\\
Attendees&Aleksander, Ida, Kristin, Lars, Magnus and Nicklas from Group 15\\
Referent&Kristin from Group 15\\
\end{tabular}

\section{Agenda approved}
\section{Minutes of meeting from last internal, customer and advisor meeting approved}
\section{Agreed ground rules}
\begin{enumerate}
\item
Everybody must work (on average per two weeks) minimum 20 hours per week, except Magnus who must work 17 hours per week.
\item
You must notify the group the day before if you know that you will be absent from the work hours we have set. The project leader has the right to ask for a reason for the absence.
\item
Deadlines must be respected, both internal and external, even if this requires extra work.
\item
Agendas, minutes and other documents that must be ready on Monday should be finished before the end of Friday (preferrably Wednesday, but cases may arrive later in the week as well). These documents will be sent to the group by mail and must be reviewed
and commented before Sunday evening.
\item
If somebody needs help or is frustrated, then that person is responsible for telling the person(s) it applies to, the project
leader or taking it up with the group. 
\item
Everyone must log work (how much and what) on JIRA before they leave. Aleksander will remind everyone at the end of the day.
\end{enumerate}
\section{Role discussion}
Most people are happy with their roles. Lars will help Kristin with the agenda and minutes.
The group roles do not mean that you alone have the responsibility for doing everything, but the overall responsibility for getting it done.
\section{Sprint 1 review}
\begin{itemize}
\item
The demo will (hopefully) be finished during the day.
\item
Positive in sprint 1
\subitem
The internal meetings are open and constructive.
\subitem
The user stories we created were OK.
\subitem
We have learned a lot about Scrum and the different frameworks we have planned to use. Some mistakes were made in the 
beginning, but we managed to take corrective actions.
\subitem
The project report has good progress.
\item
Negative in sprint 1
\subitem
We made some mistakes in the planning phase and had to replan and reestimate (create user stories and storypoints instead of
tasks and hour estimates).
\subitem
We have missed some deadlines regarding documents to the advisor and did not know until last week that
we are supposed to hand in status reports and table of effort registration weekly. 
\subitem
We might have too much bureaucracy, could probably focus our discussions more and become more productive when we meet.
\end{itemize}
\section{Sprint 2 planning}
We postphone the planning until after the customer meeting tomorrow. 
\section{Comments from Thales}
Kristin will send the feedback from Thales on the backlog on mail.
\section{Other issues}
\begin{itemize}
\item
Agendas and minutes have been converted to Latex documents and can be found on Dropbox. The documentation should still be written on Google Docs.
\item
A document on Google Docs (Weekly Routines) outlines what must be done and delivered each week of documents.
\item
Frustration and problems: Nicklas feels that he gets to little done as he must help everyone else.
\item
Documentation is the most important for the grade, but we must make the customer happy as well. We think
pre-studies and analysis is the most important documentation for the customer.
\item
Nicklas, Lars and Kristin will meet Mohsen Thursday 11:30. Place will be sent on mail.
\item
We have created a mailing list, so everyone need to check this often!
\end{itemize}
\section{Next meeting}
\end{document}