
\chapter*{Abstract}

\textbf{This report} describes the problem of communicating with the XOmail system from a mobile device and how the problem was solved. XOmail is an existing information handling and transfer system developed by Thales that focuses on security and on delivering messages to the correct destination in a short time. During the project we created an Android application for cell phones that should provide a similar level of security and stability as XOmail does on computers. The primary challenges of the project were how to make an application for handheld devices that was secure enough to send important and classified messages and to develop a user interface that was customized for small screens and easy to use.
\newline

\textbf{The motivation} behind working on this task was that even if there exist several email applications for handheld devices today, none of them support the amount of security we needed. The most interesting part of the assignment was to figure out how to implement the required level of security and to design an application suited for small handheld devices. None of us had done extensive work with the Android framework before, so we were eager to learn more about the technology. Android development is getting increasingly more attention in the development departments today, so getting the opportunity to learn about the newest technology on the market was very interesting.
\newline

\textbf{The demands} of our software project were, at a first glance, quite simple. By implementing a mobile version of XOmail, the XOXOmail client, we wanted to show how a functioning Android client might look like. It is important to note that we focused on creating a proof-of-concept messaging client that used the standards given by Thales. The primary focus was not on creating a fancy user interface, but rather on fulfilling the needs of the users.
\newline

\textbf{The result} of this project was first of all a working application that contained realizations of the better part of the requirements of the project. Secondly, the project resulted in this report, which has the purpose of documenting the problem, the process and the product.