\chapter*{Detailed contents}

\section*{Goal of the report}
This report is meant to document the entire process behind developing the XOXOmail, from planning and pre-studies through the different sprints and ending with a conclusion and reflection part. This report should describe what was done, why it was done and when it was done. The pre-studies and the decisions made from these studies are documented. It will describe the process of making the application the customer wanted. It should describe and justify the decisions and actions made, as well as sum up what went well and what we could have done better if we were to start over.

\section*{What this report covers}
\textbf{Part I - Planning \& requirements} gives an overview of the planning we did based on the  \hspace*{4.3em} requirements of the project, as well as the pre-studies, test plan and architecture. \\
\textbf{Part II - Scrum process} describes all of the sprints very carefully. It also includes the product  \hspace*{4.3em} backlog and the changelog.\\
\textbf{Part III - Conclusion \& reflection} describes the results from the project and gives reflections \hspace*{4.3em} on how the team worked together and what we have learned from this project.\\

Part I contains the following chapters:\\
\textbf{Chapter 1 - Introduction} describes the existing product, the wanted solution and gives an \hspace*{4.3em} overview of the military standards we had to conform to in our application.\\
\textbf{Chapter 2 - Project directive} describes all the involved parties in this project.\\
\textbf{Chapter 3 - Project planning} gives an overview of how this task was planned, how the team \hspace*{4.3em} was organized and the quality assurance measures of the project. \\
\textbf{Chapter 4 - Requirements} contains the functional and the non-functional requirements that  \hspace*{4.3em} describes how the application should look and behave. In addition the stakeholders of \hspace*{4.3em} the project, the use cases and the requirements draft from the customer are listed in \hspace*{4.3em} the chapter. \\
\textbf{Chapter 5 - Project study} gives summaries of all the preliminary studies done in this project, \hspace*{4.3em} as well as the decisions that were made from these studies.\\
\textbf{Chapter 6 - Test plan} explains how the code and application were tested in this project.\\
\textbf{Chapter 7 - Architectural description} describes the architecture of the application, both \hspace*{4.3em} backend and frontend.\\

\section*{How this report is structured}
The report is divided into parts as well as chapters. This gives a much better overview of the report, and makes it a lot easier to find your way around it. It is divided into three parts: a planning and requirements part, a part about the Scrum process and the conclusion and reflection part.