


\subsection{Detailed sprint plans}
This appendix contains detailed plans from each of our sprints. Which task we plan on doing and what each task represent.

\paragraph{Sprint 1}

\begin{itemize}
\item{}\textbf{Setup of Jira:}we decided to use Jiro to get an overview over all the work that we need to do. Jira also gives us an overview over what tasks are supposed to be done in each sprint. We also use Jira to assign the tasks to each of the team members.
\item{}\textbf{Report work:} the report that are to be delivered at the end of the project needs a lot of work, and we have decided that we will use time on the report in every sprint.
\item{}\textbf{Set up programming environment:} working with setup of software in administrative sense.
\item{}\textbf{Group Administration:} to administer the entire group, with booking group rooms and sending e-mails to the customer, the advisor and the team to call in for meetings.
\item{}\textbf{Meetings:}arrange meetings and the time we use on meetings.
\begin{itemize}
\item{}\textbf{Meetings with Thales:} we have weekly meetings with our customer so that we can get rapid feedback on what we do. To know if they agree on our decisions and to know that we haven’t misunderstood the tasks they give us.
\item{}\textbf{Meetings with Mohnsen Anvaari:} we have regular meetings with our advisor so that he can give us feedback on how we do our work, and make sure that we do what are expected of us in the course.
\item{}\textbf{Internal meetings:} we almost have daily meetings to know what everybody has been doing lately, and how far we have come in our task; what is left and what is done.
\item{}\textbf{Lectures:} there are some lectures during the semester, and we are recommended to join these. In this sprint there are 3 lectures and courses that we have decided to attend.
\end{itemize}
\item{}\textbf{Create interfaces between Core and GUI:} code interfaces that let GUI and core to communicate in the simplest way. We need this code to be able meet our Sprint 1 milestone. We need these interfaces to make a simple model.
\begin{itemize}
\item{}\textbf{Persistence Service Interface:} preliminary design of interfaces for the Persistence Service module.
\item{}\textbf{Hardware abstraction layer interface:} preliminary design of interfaces for the HAL Service module.
\item{}\textbf{Network Service Interface:} preliminary design of interfaces for the Network Service module.
\item{}\textbf{Security Service Interface:} preliminary design of interfaces for the Service Service module.
\end{itemize}
\item{}\textbf{General setup of tools:} general setup of different tools we use.
\item{}\textbf{Meeting and agenda document writing:} to write all the minutes and agendas using the right template.
\item{}\textbf{Starting App:} making our program good enough so that it is possible to start the program and begin browsing all features of the program.
\begin{itemize}
\item{}\textbf{Create Main menu:} make a simple main menu with a header showing the name of the program and a list containing all views it is possible reach from the menu.
\item{}\textbf{Create a basic android app skeleton:} make an Android app project so that we have a running application with nothing in it.
\item{}\textbf{Learn how Android MVC works:} find out how Android MVC works and get a general feeling of how the layout of the Android project will be.
\end{itemize}
\item{}\textbf{Sending a message:} the user should be able to click the “New message” button, be brought to the new message page, create a message and send it pressing the “Send” button.
\begin{itemize}
\item{}\textbf{Adding subject and text to a message:} create a simple GUI making the user able to create a message with a title and a text and sending it to a recipient. At first it is enough to send to a predefined receiver until the address book is made.
\item{}\textbf{Make connection between “Send Message” button and backend:} make the GUI communicate with the backend responsible for sending the actual message.
\item{}\textbf{Implement a Network class for sending e-mail through gmail’s smtp-server:} implement an instance of the NetworkService interface which sends mail via gmail’s mail servers.
\item{}\textbf{Create the new message view:}make it able for the user to get a view showing all fields relevant to creating a message by clicking “New message”.
\item{}\textbf{Implement receiving mail from gmail’s imap-service:} make the app able to receive the mail automatically from Gmail’s Imap, as soon as a message is received at the account. This must be done via push to client, not pull.
\item{}\textbf{Create core bridge:} does the connection from GUI to core and returns value from implemented interface on core side.
\end{itemize}
\item{}\textbf{Persisting data to phone:} Implement persistence, so that the app is able to save data and retrieve it whenever it wants.
\begin{itemize}
\item{}\textbf{Research on structure for saving and reading data}: find a structure for saving data to the phone. What is the best way of organizing data with respect to files created by app, file settings and other files?
\item{}\textbf{Save data to phone storage:} ensure proper saving of data to phone.
\item{}\textbf{Read data from phone:} ensure proper saving of data to phone.
\end{itemize}
\end{itemize}

\paragraph{Sprint 2}

\begin{itemize}
\item{}\textbf{Report work:} the report that are to be delivered at the end of the project needs a lot of work, and we have decided that we will use time on the report in every sprint.
\item{}\textbf{Group Administration:}to administer the entire group, with booking group rooms and sending e-mails to the customer, the advisor and the team to call in for meetings.
\item{}\textbf{Meetings:}arrange meetings and the time we use on meetings.
\begin{itemize}
\item{}\textbf{Meetings with Thales:} we have weekly meetings with our customer so that we can get rapid feedback on what we do. To know if they agree on our decisions and to know that we haven’t misunderstood the tasks they give us.
\item{}\textbf{Meetings with Mohnsen Anvaari:} we have regular meetings with our advisor so that he can give us feedback on how we do our work, and make sure that we do what are expected of us in the course.
\item{}\textbf{Internal meetings:} we almost have daily meetings to know what everybody has been doing lately, and how far we have come in our task; what is left and what is done.
\item{}\textbf{Lectures:} there are some lectures during the semester, and we are recommended to join these. In this sprint there are 2 lectures and courses that we have decided to attend.
\end{itemize}
\item{}\textbf{Browse previously sent messages:} make it possible to see all messages that are previously sent, so that it is possible for the user to check that they actually were sent.
\begin{itemize}
\item{}\textbf{Show basic listing of all elements in list:} a basic listing of all elements will be implemented, and each data element in the list should have all necessary fields that are required.
\item{}\textbf{Style elements in list:} use design to make all the elements look nice.
\end{itemize}
\item{}\textbf{Meeting and agenda document writing:} to write all the minutes and agendas using the right template.
\item{}\textbf{Sending a message:} the user should be able to click the “New message” button, be brought to the new message page, create a message and send it pressing the “Send” button.
\begin{itemize}
\item{}\textbf{Implement metadata structure and show it:} implement all the fields that are required to send a message; from, to, classification, label, priority, and make them look nice.
\end{itemize}
\item{}\textbf{Browse inbox:} the user should be able to show a list of all received messages, both read and unread.
\begin{itemize}
\item{}\textbf{Show basic listings of all mails received:} implement a basic list of all elements, and make sure that all necessary fields that are required shows.
\item{}\textbf{Style elements in list:} style each element of the list, so that it is pleasing to look at.
\end{itemize}
\item{}\textbf{Read message:} making the user able to read a message.
\begin{itemize}
\item{}\textbf{Showing all metadata:} implement all fields that are related to a message, and show them.
\item{}\textbf{Showing all message subject and text:} show all fields that are related to a message; date received, from. 
\item{}\textbf{Reply/Delete/Forward:} implement the buttons so that the user can reply to a message, delete a message and forward a message.
\end{itemize}
\item{}\textbf{Browse outbox:} the user should be able to show a list of all messages that are waiting to be sent, or haven’t been sent yet.
\begin{itemize}
\item{}\textbf{Show basic listing of all elements in list:} implement a basic listing of all elements, and that each data element in the list has all necessary fields that are required.
\item{}\textbf{Style list for pretty viewing:} make the list look nice.
\end{itemize}
\item{}\textbf{Bottom menu bar:} implement the bottom menu bar so that a user can switch between pages using the menu bar.
\begin{itemize}
\item{}\textbf{Create bottom menu bar:} implement the menu bar and make it nice by applying design.
\end{itemize}
\item{}\textbf{Security Pre-study:} dig deeper into the security aspects of Android, in order to make well informed decisions.
\begin{itemize}
\item{}\textbf{Secure sending:} write security documentation on secure sending.
\item{}\textbf{Secure storage on phone:} write documentation regarding secure storage of data and password.
\item{}\textbf{Signing and verification:} finding out how secure signing works, and write documentation on it.
\item{}\textbf{Limitations and facilities of Android:} what are the limitations regarding Android Security, and what does Android facilitate when it comes to encapsulation? Are data in memory secure? Find the answers to the questions and document it.
\item{}\textbf{Security requirements:} write a summary from the documentation linked to by Tellefsen.
\end{itemize}
\item{}\textbf{Architecture documentation:} make an architectural description document, so that I know that my code fulfills all the requirements.
\begin{itemize}
\item{}\textbf{Fulfillment of requirements:} describe how our architecture fulfills the security, usability and latency requirements.
\item{}\textbf{Graphical view of architecture:} create a graphical view of the architecture, both backend and frontend.
\item{}\textbf{Frontend:} document the frontend properly.
\item{}\textbf{Backend:} document the backend properly.
\end{itemize}
\end{itemize}
