\subsection{Limitations}
In this section it will be described both the technical and non-technical limitations the group had to deal with in the project.

\subsubsection{Technical limitations}
The technical limitations is limitations for our project according to technical difficulties.
\paragraph{Android}\hfill
\newline
Android is a quite new platform and none of us have been doing much programming with this framework prior to this project. The task of learning how Android worked and to find technical tools that Android supports was going to be a time consuming task. We wanted to develop our project in Android version 2.2 with \gls{api} level 8. The reason behind choosing this version of Android was that we did not want to depend on features that only existed in newer versions of Android, and 2.2 is a version that is very common.

\paragraph{Android security limitations}\hfill
\newline
Using Android as our platform gives us a number of limitations when it came to security. Firstly, the device is small and easy to lose compared to a fixed installation such as a computer. Secondly, we need to rely on existing civilian network rather than purpose-built military communication channels.
\newline
\newline
A major issue for our security considerations is the mobility of XOXOmail. The small device could easily be lost or stolen and fall into the wrong hands, so we have to take this into account when developing for security. We therefore plan to encrypt the entire phone and require a login on system resume, with a short timer.
\newline
\newline
An Android-based application is problematic in that it communicates over the Internet, thus it is conceivable that someone could listen in to the transmissions from the application. We plan to resolve this through the use of network layer encryption through \gls{ssl1}. 

\paragraph{Screen}\hfill
\newline
The mail client is going be used on devices with relatively small touch screens, which means that the application must be carefully designed to accommodate the limited size. In addition we need to put a lot of thought into the design so that it becomes easy to use. The application must be designed to scale well with different screen resolutions.

\subsubsection{Non-technical limitations}

\paragraph{Language}\hfill
\newline
The entire project is to be delivered in English, so we all have to write in our second language. This means that the report work would take more time than if we could write it in Norwegian. 

\paragraph{Duration}\hfill
\newline
We have a set timeframe of 13 weeks with a delivery deadline that can not be changed. This gives us a set amount of effort and we probably do not have the time to implement all the desired parts of the application. We have to focus on the parts we find most important. The specified timeframe will likely give us challenges when it comes to planning and priorities of the different tasks.