\chapter{Product Backlog}
\section{Product backlog}
The product backlog is an ordered list of ``requirements'' for the project. Aspects taken into consideration when ordering the backlog include business value and dependencies.\\\\
		Each entry in the backlog is on the form:\\
			\indent {\it Priority }{\bf Title(Complexity in storypoints)} {\it Description}
		
		\begin{enumerate}
			\item {\bf Starting the app\SP{5}} As a user, I should be able to start the program so that i can begin browsing all features of the program
			\item {\bf Create interface between core and gui\SP{13}} As a programmer, I will make the interfaces that is needed so that the service and gui can communicate in a simple way, making it easy for GUI programmers to start using code that has not been written yet.
			\item {\bf Persisting data to phone\SP{17}} As a programmer I will have to implement persistence, so that the application is able to save data and retrieve it whenever it wants.
			\item {\bf Sending a message\SP{13}} As a user, I should be able to click the ``New message'' button, so that I am brought to the new message page, making me able to create a message and pressing ``Send'' to send it to a user
			\item {\bf Browse previously sent messages\SP{13}} As a user, I want to see all messages that I have previously sent, so that I can check their status.
			\item {\bf Browse inbox\SP{13}} As a user, I should be able to review all previous received messages.
			\item {\bf Browse outbox\SP{13}} As a user, I should be able to review all previous sent messages.
			\item {\bf{Read message\SP{11}}} As a user I should be able to show the list of all messages received, both read and unread.
			\item {\bf Bottom menubar\SP{5}} As a user I should be able to use the bottom menubar to switch between pages. This should include {\it inbox}, {\it outbox}, {\it emergency messages} and {\it new messages}
			\item {\bf Architecture documentatio\SP{40}} As a programmer I would like to have an architectural description document, so that I know that my code fullfills all requiremetns.
			\item {\bf Security prestudy\SP{40}} As a developer I should research the security aspects of Android, in order to make well informed decisions.
			\item {\bf 2. iteration, Networkservice\SP{13}} As a programmer I should extend the communication implementation to support more features, so that we can have message priorities, message types, message grading, message status and notification of failed deliveries.
			\item {\bf Receiving messages with attachments\SP{15}} As a user I should be able to receive a message with an attachment and open the attachment
			\item {\bf Sending messages with attachments\SP{13}} As a user I should be able to add an attachment to the message I want to send , so that the recipient gets my attachment as well as the message.
			\item {\bf Log in to application\SP{13}} As a user, I should be able to log in via the login screen so that after this process I am an authorized user inside the program.
			\item {\bf Answer, delete and forward a message\SP{8}} As a user I want to be able to utilize the ``Answer'', ``Delete'' and ``Forward'' features that is associated with each message so that i am brought to the correct screen for each of these operations.
			\item {\bf Add signing to messages\SP{20}} As a programmer I should be able to create or use an existing library for digital signing and verification of messages.
			\item {\bf Compression algorithm\SP{13}} As a programmer I want to be able to create or find a library that minimizes data traffic that is needed to send a message so that the messages are sent faster over low speed internet connections.
			\item {\bf Settings menu\SP{8}} As a user, I should be able to utilize the settings menu to alter different settings of the app, so that I have the settings set to what I prefer.
			
			
			
			\item {\bf Viewing address book\SP{8}} As a user I should be able to view my address book with all of my contacts, so that I am able to choose a recipient from a list when I want to send a message.
			\item {\bf Secure communications channel\SP{5}} As a programmer I should implement a wrapper that makes the communication with the server secure.
			\item {\bf Implement hardware abstration layer\SP{20}} As a programmer I will implement the hardware abstraction layer, so that I can use the phones physical input\/output devices, as GPS, camera, video and sound.
			\item {\bf Distribution of addressbook\SP{13}} As a programmer, I should be able to distribute address books between each of the users via LDAP or Control message so that all users have an address book with all users.
			\item {\bf Message templates\SP{17}} As a user, I should be able to choose a template for a message with all relevant information is predefined, as well as creating new ones, so that I can send a message without writing anything at all.
		\end{enumerate}
		\section{Changelog}
		\begin{description}
			\item[\dateFormat{10}{31}{2012}] Revised product backlog, removing elements no longer relevant to us.
			\item[\dateFormat{10}{08}{2012}] Renamed BL18 'Extends communication interface' to 'Networkservice, 2.iteration'
			\item[\dateFormat{09}{24}{2012}] Inserted new backlog elements BL6 to BL11, to incorporate a shift in focus for sprint 2. Updated goal for sprint 2, removed goals for sprint 3 and 4. Sprint planning for sprint 2 added.
			\item[\dateFormat{09}{12}{2012}] Rewrite of document. Changed from taskdescriptions to stories in backlog, added storypoints for each entry. 
			\item[\dateFormat{09}{06}{2012}] Goals added to each sprint. BL5 (Message template) moved down in backlog as requested from customer.
			\item[\dateFormat{09}{04}{2012}] Sprint planning for sprint 1 added
			\item[\dateFormat{08}{28}{2012}] Backlog pdf created
		\end{description}