
\begin{longtable}{>{\setlength\hsize{.3\hsize}}X|>{\setlength\hsize{0.7\hsize}}X|>{\setlength\hsize{.3\hsize}}X}\hline
\textbf{Req. ID} & \textbf{Description} & \textbf{Priority} \\ \hline \hline

\textbf{FR1} & \textbf{Starting application and logging in:} The user has to be able to start the application and authorize himself against an authorizing mechanism. & High \\ \hline
\textbf{FR2} & \textbf{Send a message to another user:} The user has to be able send a simple message via regular email protocols to a recipient of own choice. & High \\ \hline
\textbf{FR3} & \textbf{Browse received messages:} The user has to be able to browse all messages he has received. & High \\ \hline
\textbf{FR4} & \textbf{Browse sent messages:} The user has to be able to browse all messages he has sent.& High \\ \hline
\textbf{FR5} & \textbf{Viewing address book:} The user has to be able to view the address book with all contacts, so that he is able to choose a recipient from a list when he wants to send a message. & High \\ \hline
\textbf{FR6} & \textbf{Marking messages with military attributes:} The user has to be able to set security label, message priority and message type on a message, so that the receiver of the message knows who the message is intended for, how important it is and in what environment it is is of interest. The message priority will decide how intrusive XOXOmail is, that is, how much the app takes over the phone in order to show the user that a message has arrived.  & High \\ \hline
\textbf{FR7} & \textbf{Sending and receiving message with attachments:} The user has to be able to add an attachment to the message, so that the recipient gets the attachment as well as the message. By opening the message, the attachments will also show. & Medium \\ \hline
\textbf{FR8} & \textbf{Answer, delete and forward messages:} The user has to be able to, by clicking on a message, choose if he wants to answer, delete or forward the message, and be brought to the correct screen for doing the selected action. & Medium \\ \hline
\textbf{FR9} & \textbf{Send instant message:} The user has to be able to, via very few screen interactions, send an instant message with a predefined security label and priority, to a predefined list of recipients. & Medium \\ \hline
\textbf{FR10} & \textbf{Settings menu:} The user has to be able to alter the following settings: 
\begin{itemize}
\item{}Change between push and pull strategy
\item{}Choose which security labels should be visible in the view for sending a message, if the user does not want to have all the choices
\item{}Settings for instant message standards
\item{}Change default values of dropdown menus in the New Message window.
\end{itemize}  & Low \\ \hline
\textbf{FR11} & \textbf{Message status:} The user has to be able request a receipt notification and delivery report for a message and to see the status of a message where this is requested.& Medium \\ \hline
\textbf{FR12} & \textbf{Viewing high priority message} The user should, when a message with priorities flash/override is received, be able to be notified directly and open the message with few actions. & High \\ \hline
\textbf{FR13} & \textbf{Sorting the messages:} The user has to be able to sort the messages according to different criterias, e.g. date, sender, priority etc. & Medium \\ \hline
\textbf{FR14} & \textbf{Searching in the message folders:} The user has to be able to search based on different criterias to quickly find messages in the message folders. & Low \\ \hline
%\newpage
%\newpage

\caption{Functional requirements} \label{tab:functionalrequirements}
\end{longtable}