\chapter{Sources}

\begin{enumerate}
\item{} Thales Norway AS. Retrieved 2012-08-28 from 
\newline
<http://www.thales.no/pub/sites/index.php?siteID=4\&m=1>
\item{} Java (Programming Language). Retrieved 2012-09-10 from
\newline
<http://en.wikipedia.org/wiki/Java\_programming\_language>
\item{} Android Native Development Kit (NDK). Retrieved 2012-09-10 from <http://developer.android.com/tools/sdk/ndk/index.html>
\item{}PHP for Android (PFA). Retrieved 2012-09-10 from 
\newline
<http://phpforandroid.net/manual/en/index/faq>
\item{}Scripting Layer for Android (SL4A). Retrieved 2012-09-10 from 
\newline
<http://code.google.com/p/android-scripting/>

\item{}Monodroid by Xamarin. Retrieved 2012-09-10 from 
\newline
<http://xamarin.com/monoforandroid>
\item{}Extensible Markup Language (XML). Retrieved 2012-09-10 from 
\newline
<http://en.wikipedia.org/wiki/Xml>
\item{}JavaScript Object Notation (JSON). Retrieved 2012-09-10 from 
\newline
<http://www.json.org/xml.html>
\item{}Agile Software Development And Scrum. Retrieved 2012-09-10 from
\newline
<http://www.mountaingoatsoftware.com/topics/scrum>
\item{}Scrum (Development). Retrieved 2012-09-10 from 
\newline
<en.wikipedia.org/wiki/Scrum\_(development)>
\item{}Git and GitHub. Retrieved 2012-09-10 from <https://github.com/>
\item{}Service http://developer.android.com/reference/android/app/Service.html
\item{}AIDL http://developer.android.com/guide/components/aidl.html
\item{}IBinder http://developer.android.com/reference/android/os/IBinder.html


\end{enumerate}


