\section{Sprint 4 - Conclusion}
After the completion of the fourth and final sprint we had a product that met the requirements from Thales and presented itself in a manner that we could be proud of. We also reached a point where the report had a complete feel to it with the elements we thought important were included. 
\newline
\newline
While performing the fourth sprint we worked rather sporadically with a lot of different tasks resulting in a sort of “chaotic” progression. This was more or less the only way to get things done because of the variation of the tasks. Even though we had to work in a somewhat different manner with regards to prior sprints, we managed to keep the workload under control and complete most of the tasks set for the sprint. The work distribution in this sprint was based on who that was most suited to perform the tasks as we needed tasks to be completed fast and with quality. Some of the group members were given tasks that were larger and more demanding than other tasks, but there were a lot of smaller tasks as well that could be distributed to remaining group members. This approach worked rather well and we completed most of the goals we had set.
\newline
\newline
This sprint had a bigger workload then the sprints performed in the past and and required us to put in some extra effort in order to finish it in a respectable way. We had some problems estimating the tasks because they varied so much. This resulted in some extra time being spent on tasks that were underestimated. We managed to finish all of the larger tasks included in this sprint and most of the minor ones. This left us in a solid position at the end of the sprint. We had finished the report and application as well as being ready to present our project. We were pleased with how this sprint ended up.    



