\section{Sprint 3 - Ordered sprint backlog}

\begin{itemize}
\item{}\textbf{Report work:} the report that is to be delivered at the end of the project needs a lot of work, and we have decided that we will use time on the report in every sprint.
\item{}\textbf{Meetings:}arranging meetings and the time we use on meetings.
\begin{itemize}
\item{}\textbf{Meetings with Thales:} we have weekly meetings with our customer so that we can get rapid feedback on what we do. To know if they agree with our decisions and that we haven't misunderstood the task thay have given us.
\item{}\textbf{Meetings with Mohnsen Anvaari:} we have regular meetings with our advisor so that he can give us feedback on how we are doing our work, and make sure that we do what are expected of us in the course.
\item{}\textbf{Internal meetings:} we have almost daily meetings to learn what everybody has been doing lately, and how far we have come in our tasks; what is left and what is done.
\item{}\textbf{Lectures:} there are some lectures during the semester, and we are adviced to paticipate in these. In this sprint there are 2 lectures and courses that we have decided to attend.
\end{itemize}
\item{}\textbf{Meeting and agenda document writing:} to write all the meetings agendas and minutes using the right template.
\item{}\textbf{Receiving message with attachment:} as a user I should be able to receive a message with an attachment and to see the attachment.
\begin{itemize}
\item{}\textbf{Study:} how should we show the different attachments? Use some embedded features of android or use our own? Are the attachments shown immediately or do we click a button to show it? Do some studies so that you are able to answer all the questions above.
\item{}\textbf{Implement:} implement showing attachments based on what was found out in the study. What this task involves, depends on which attachments we receive. A picture will be shown differently than GPS coordinates. Maybe the coordinates should be implemented into the message body, while the image will be shown by a button, as figured in the above study task.
\item{}\textbf{Document:} document the different options that are found relevant for the solution of the task, but was excluded due to complexity or because it was a bad alternative.
\end{itemize}
\item{}\textbf{Instant message:} the user should be able to send an instant message using only three touches.
\begin{itemize}
\item{}\textbf{Find design solution:} find out how to implement the instant message feature. Where should the instant message button be placed? What is the fastest solution? How should the send instant message window look like?
\item{}\textbf{Incorporate instant message button into GUI:} get a working button in the GUI that takes the user to the instant message view.
\item{}\textbf{Create send instant message view:} create a view that is to be used for sending an instant message, based on what is found to be the best design solution.
\end{itemize}
\item{}\textbf{Delete message:} the user should be able to delete a message that is received.
\begin{itemize}
\item{}\textbf{Delete from local storage:} Implement the response of deleting a message locally whenever a user wants to delete the message.
\item{}\textbf{Delete from mail server:} Implement the response of deleting a message from the mail server whenever a user wants to delete the message.
\item{}\textbf{Update GUI:} Implement the response of removing a message from the gui whenever a delete operation is completed. 
\end{itemize}
\item{}\textbf{GUI-Issues:} revisions of the GUI based on input from Thales.
\begin{itemize}
\item{}\textbf{Menu:} the top menu bar must be made smaller by removing the text, and only use pictures.
\item{}\textbf{Header:} remove the header saying XO-mail. It is not necessary.
\item{}\textbf{Change security labels to upper case:} all the security labels should be of the format CAPS\_LOCK! Upper case and underscore for spaces.
\end{itemize}
\item{}textbf{Evaluation:} Write an evaluation of the project.
\item{}textbf{Presentation:} Make a presentation to show for the examinator.
\end{itemize}