\chapter{Sprint 1}

This chapter is meant to give an overview of sprint 1. Section 9.1 gives an overview of the sprint. Section 9.2 gives the duration of the sprint. Section 9.3 describes the concrete project work plan of the sprint. Section 9.4 describes the goal of the sprint. Section 9.5 details the ordered sprint backlog. Section 9.6 details the system design at the end of the sprint. Section 9.7 describes the feedback given by Thales on the sprint results. Section 9.8 gives an overview of how the hours were spent in the sprint. Section 9.9 closes the chapter off with a final conclusion on the sprint. The other sprint chapters are structured in a similar way.

\section{Sprint 1 - Planning}
The time leading up to Sprint 1 was spent looking into different solutions and agreeing on details such as programming language, development tools and top level architecture. We also spent a large part of the week setting up various tools on our personal computers; especially accounting for the wide variety of hardware and operating systems.
\newline
\newline
Sprint 1 was our first major coding spree. We set aside some time to set up all the required software and communications on the last few computers, but most of the time was to be spent putting together a rough prototype. Our goal was to be able to send and receive messages from the phone by the end of the sprint (fulfilling most of customer requirement 3.3), providing us with a functional framework we could bolt our later expansions on to. Tasks like security and intuitive \gls{gui} were saved for later sprints.
\newline
\newline
As well as the coding, which was to be largely handled by three of us in this first sprint, a lot of time was scheduled for theoretical studies. Things to be implemented later had to be researched and documented, and lot of basic things like agenda templates and documentation structure had to be set up.