\chapter{Sprint 4}

\section{Sprint 4 - Planning}


Completing the third sprint left us with a functional application that we could use to demonstrate the potential of a future product. Since we now had completed most of the coding planned for this project we could switch the focus towards completing the report and start preparing for the presentation to be held at the end of the project span.
\newline
\newline
After a meeting with Thales where we gave them a quick demonstration of the application, we received some feedback on 3 areas that needed minor additions. These included the ability to receive messages properly from Thales' system, taking a picture and sending it directly from outside the application and changing the priority listing of messages in the inbox from numbers to the equivalent letter code. We also agreed that after completing these 3 additions the application prototype was finished and that there was no room for further development.
\newline
\newline
The tasks to be done in the fourth sprint evolved highly around the report and the final presentation. The report contained a lot of areas that needed additional information and/or figures and some sections were still to be written. Since the presentation is an important part of the this project we also needed to dedicate a reasonable amount of time to the planning of the presentation. There was also room to perform some product testing outside of the project group consisting of user test-cases that needed a run-through. We realized that this sprint consisted of many tasks that had a great variation in size and duration. We therefore assigned the tasks on the go to whoever was available and most suited at that time.
\newline
\newline
After this sprint; the report, application and presentation needed to be more or less finished since we only had 3 days after the end of sprint to make the final adjustments. We realized that this final sprint would be tough and require some more hours put in than the prior sprints. This was needed in order to end up with a complete solution. 
      