\section{Sprint 2 - System design}
After the second sprint, the system worked in the following way: A user opens XOXOmail on his phone. He is then brought directly to a tab called “Folders” which at first displays all the inbox messages of the application.
\newline
\newline
In the \textsc{Folders tab}, the user gets the opportunity to choose either  \textsc{Inbox},  \textsc{Outbox} or  \textsc{Sent} from a dropdown menu.  \textsc{Inbox} shows a list of received messages, which the user can read one by one by clicking them. \textsc{Sent} takes the user to a list of sent messages which works in the same way as \textsc{Inbox}. \textsc{Outbox} is in this iteration not yet implemented. There is also a button that is called sort, which is also not implemented.The backend of this feature works in the same way as it did after the first sprint. 
\newline
\newline
If the user selects the \textsc{New Message} tab, he is taken to the message creation screen where he can add recipients and subject to the message. In this iteration we also included the functionality of adding attributes to the messages sent (Security Label, Message Priority and Message Type). The attributes are sent along with the message in the message header.
\newline
\newline
The changes to XOXOmail with respect to functionality in sprint one, is the addition of attributes to the messages and the menu bar at the top. It is all now packed into a better user experience where the number of errors a user can do is a lot fewer. 
