\chapter{Sprint 3}

\section{Sprint 3 - Planning}
After finishing the second sprint we ended up with a lot more documentation and as a result of this a more general understanding of how XOXOmail should function when considering both the frontend and backend part. As we had become \textit{a jour} with most of the documents we could start planning a sprint that had more focus on the actual application and the features that it should include. 
\newline
\newline
After meeting with Thales we ended up with two areas that we agreed to make the main focus in the third sprint. One of the two was the ability to connect XOXOmail with a test-server provided by Thales (as per customer requirement 2.3), the other was to implement the feature of receiving and sending messages with an attachment
\newline
\newline
In this sprint we also made room for several application features in the customer requirements that had not yet been implemented. This included:
\begin{itemize}
\item{}Logging in to the application (FR1)
\item{}Answering and forwarding messages (FR8)
\item{}Adding signing to messages (FR14)
\item{}Adding a settings menu (FR10)
\item{}Sending instant messages (FR9)
\item{}Deleting received messages (FR8)
\item{}Miscellaneous graphical user interface design issues
\end{itemize}

We also wanted to see how the application worked on a lower network layer, so we planned to perform a Wireshark analysis of the application regarding the sending and receiving part of the system. 

\newpage

Most of the tasks to be solved in the third sprint involved a lot of programming. This resulted in many tasks that had an uncertain time estimate. Sometimes a solution comes to life with little bugs and issues, other times a seemingly easy task can take up a lot of time due to unforeseen problems. We did however acknowledge that this sprint was going to have a heavy focus on the programming and that there were many tasks to complete. We therefore put most of the group on the various programmatic problems whilst having one group member continuing the report work. We also had one person that concluded the Wireshark analysis in between the other programming tasks. 
\newline
\newline
With the completion of sprint 3 we hoped to be more or less done with developing the application so that we could focus on the documentation in the fourth and final sprint. This was important because much of the added functionality needed to be documented along with many of the choices taken.
