\section{Unit testing frameworks}

Unit testing is a method where individual units of source code are tested to determine if they are fit for use. These units consist of sets of one or more computer program modules together with their associated control data, usage procedures, and operating procedures \cite{bib:kolawa}.

\subsection{JUnit}
JUnit is a testing framework for Java programming language, and is a member of the xUnit collective. Therefore a JUnit test fixture is a Java object, and all the test method must be annotated by the @Test annotation. JUnit is linked as a JAR at compile time. With JUnit you must write your own tests, and you can run many tests at the same time. JUnit is a great tool to use for testing Java code \cite{bib:junit}.

\subsection{Mockito}
Mockito is an open source testing framework for Java that allows creation of Test Double objects called “Mock Objects”. Mock Objects are simulated objects that mimic the behavior of real objects in a controlled way \cite{bib:mock}.
\newline
\newline
Mockito distinguishes itself from other mocking frameworks by allowing developers to verify the behavior of the system under test (SUT), without establishing any expectations beforehand \cite{bib:mockito}.
One of the criticisms of mock objects are that there is a tight coupling of the test code to the system under test \cite{bib:mocks}.

\subsection{GreenMail}
GreenMail is the first and only library that offers a test framework for both receiving and retrieving emails from Java.It is an open source, intuitive and easy-to-use suite of email servers used for testing purposes. It supports SMTP, POP3 and IMAP with SSL socket support \cite{bib:greenmail}.

\subsubsection{Useful for:}
\begin{itemize}
\item{}Test your sending code: 
\begin{itemize}
\item{}GreenMail responds like a regular SMTP server but does not deliver any email, which enables it to be used in real life applications and real test cases. 
\item{}Messages can easily be extracted, verified, and modified. 
\item{}GreenMail is an excellent choice for unit testing code that needs to send email with a succinct, efficient way to wait for messages to arrive, retrieve, verify, and modify messages. 
\end{itemize}
\item{}Test your retrieving code: 
\begin{itemize}
\item{}GreenMail can be used for system or unit testing an application that needs to use POP3 or IMAP, by responding like a standard compliant POP3 or IMAP server. 
\item{}Messages can be placed directly in user mailboxes or by using SMTP.
\end{itemize}
\end{itemize}

\subsubsection{Sending and Retrieving}
GreenMail can easily be configured to use all or a combination of ports, protocols, and bind addresses. It  is possible to run GreenMail on SMTP, POP3, POP3S and IMAPS ports as easily as only with SMTP. Many systems might already be running these servers or don’t allow non root users to open the default ports which is why GreenMail ships with a special configuration for testing.