\documentclass[a4paper,12pt]{article}
\usepackage{array}
\begin{document}
\title{Agenda for Internal Meeting \#4}
\maketitle
\begin{tabular}{>{\bfseries}l l}	
Project name&Formal and secure messaging on a mobile platform\\
Calling by&Group 15\\
Time and date&2012-09-18 08:15\\
Place&R30\\
Attendees&Aleksander, Ida, Kristin, Lars, Magnus and Nicklas from Group 15\\
Referent&Kristin from Group 15\\
\end{tabular}

\section{Approval of agenda}
\section{Approval of minutes of meeting from last internal, customer and advisor meeting}
\section{Set ground rules for the project}
\begin{enumerate}
\item
Everybody must work (on average) at least 20 hours per week.
\item
One must have a good reason (things that are required) to be late, leave early or be absent. 
\item
Deadlines must be respected, both internal and external, even if this requires extra work.
\item
Agendas, minutes and other documents that must be sent Monday 14:00 should be ready before the end of Friday. 
The rest of the group must review the documents and give comments before Sunday evening. 
\item
It is understandable that other courses also take time, but this is the same for all of us.
It might require us to work after school and in weekends.
\item
If somebody needs help, is frustrated or is stuck, that person is responsible for telling the project leader or the group. 
\end{enumerate}
\section{Role discussion}
\begin{itemize}
\item
Are people happy with the role allocation? There is an uneven distribution of roles. 
\item
Everybody must probably participate in many different tasks (especially towards the end)
\end{itemize}
\section{Sprint 1 review}
\begin{itemize}
\item
What is the status of the demo?
\item
What was good in sprint 1?
\item
What could have been done better in sprint 1?
\end{itemize}
\section{Sprint 2 planning}
\begin{itemize}
\item
Suggest sprint plan (Thales must be integrated more)
\end{itemize}
\section{Comments from Thales}
\begin{itemize}
\item
Lacking point in backlog
\item
Wants discussion on priorities before sprint 2 planning
\end{itemize}
\section{Other issues}
\begin{itemize}
\item
Documents on Dropbox
\item
Issue log
\item
Frustrations and problems
\item
What do you think is important to prioritize next?
\item
What makes you happy?
\end{itemize}
\section{Next meeting}
\end{document}