\documentclass[a4paper,12pt]{article}
\usepackage{array}
\begin{document}
\title{Minutes of meeting for advisor meeting \#3}
\maketitle
\begin{tabular}{>{\bfseries}l l}	
Project name&Formal and secure messaging on a mobile platform\\
Calling by&Group 15\\
Time and date&2012-09-25 11:15-11:30\\
Place&ITV-464\\
Attendees&Mohsen Anvaari from IDI\\
 & Aleksander, Ida, Kristin, Lars, Magnus og Nicklas from Group 15\\
Referent&Kristin from Group 15\\
\end{tabular}
\section{Agenda approved}
\section{Minutes of meeting from last advisor meeting approved}
\section{Comments to the minutes from last customer meeting}
\section{Approval of the status report}
\subsection{Summary}
\subsection{Work done in this period}
Status of the documents that are being created:
\newline
Group 15 thinks that they are ahead of the schedule when it comes to documentation.
The group will make architecture (probably according to the 4+1 method) within the next 
advisor meeting.
\newline
\newline
Meetings
\newline
\newline
Other activities
\subsection{Problems}
What is interfering with the progress or taking resources? Problems are often risks that have taken effect.
\newline
The challenge is to create architectural views and implement them.
\subsection{Planning of work for the next period}
Meetings\\*
Activities
\subsection{Other}
\begin{itemize}
\item
Task distribution: Everybody can pick tasks at JIRA, but someone is working more back-end and some more front-end. We
have one person responsible for the documentation, but everybody must write their parts.
\item
Document review procedure is that everybody reads the documentation and comment in 
Google Docs. 
\item
JIRA has issue tracking, and we are doing test-driven development
\item
The group has written a test plan, altough this is a high-level plan.
\item
The group can add content after the pre-delivery, the pre-delivery 
is to show that we are on the right track.
\item
The problem description can be very high-level, perhaps a paragraph.
\end{itemize}
\section{Review/approval of attached phase documents}
\section{Other issues}
\section{Next meeting}
\end{document}