\documentclass[a4paper,12pt]{article}
\usepackage{array}
\begin{document}
\title{Minutes of meeting for advisor meeting \#2}
\maketitle
\begin{tabular}{>{\bfseries}l l}	
Project name&Formal and secure messaging on a mobile platform\\
Calling by&Group 15\\
Time and date&2012-09-04 11:15-11.30\\
Place&ITV-464\\
Attendees&Mohsen Anvaari from IDI\\
 & Aleksander, Ida, Kristin, Lars, Magnus og Nicklas from Group 15\\
Referent&Kristin from Group 15\\
\end{tabular}
\section{Agenda approved}
\section{Minutes of meeting from last advisor meeting approved}
\section{Comments to the minutes from last customer meeting}
The last customer meeting was mostly a discussion of details of the requirements document the group have received from Thales. The group will send this document to Anvaari with the next minutes of meeting.
\section{Approval of the status report}
Anvaari thinks the project plan delivered is very high-level, and group 15 will create a more detailed project plan before the next advisor meeting. The group has made a product backlog and decided tasks to be contained in sprint 1. \\*
Concerning the risk plan, Anvaari recommends the group to have a plan for when a problem occurs, not just how to avoid it. The group may need to have several people responsible for a risk, e.g. if the first responsible person is absent. \\*
Anvaari's advice was to write documentation early. 
\section{Review/approval of attached phase documents}
\section{Other issues}
\begin{itemize}
\item
The group wondered whether it is OK to use previous years' reports as inspiration for headers and organization. Anvaari responded that the group might look at the reports to get an idea what can be included, but it is probably not a good idea to copy it uncritically. The reports may have missing parts and different focus from the group's project.
\item
Anvaari gave the advice to document both product and process. Similar solutions must be explained, e.g. in a table to compare the different solutions and their strengths and weaknesses.
\item
The group is going to program in Java for the Android platform
\end{itemize}
\section{Next meeting}
Tuesday 2012-09-18 11:15 at ITV-464
\end{document}