\documentclass[a4paper,12pt]{article}
\usepackage{array}
\begin{document}
\title{Minutes of meeting for advisor meeting \#1}
\maketitle
\begin{tabular}{>{\bfseries}l l}	
Project name&Formal and secure messaging on a mobile platform\\
Calling by&Group 15\\
Time and date&2012-08-22 15:15-15.30\\
Place&ITV-464\\
Attendees&Mohsen Anvaari from IDI\\
 & Aleksander, Ida, Kristin, Lars, Magnus og Nicklas from Group 15\\
Referent&Kristin from Group 15\\
\end{tabular}
\section{Agenda approved}
\section{Minutes of meeting from last advisor meeting approved}
\section{Comments to the minutes from last customer meeting}
\section{Approval of the status report}
\subsection{Summary}
\subsection{Work done in this period}
Status of the documents that are being created\\*
Meetings\\*
Other activities\\*
\subsection{Problems}
What is interfering with the progress or taking resources? Problems are often risks that have taken effect.
\subsection{Planning of work for the next period}
Meetings\\*
Activities
\subsection{Other}
\section{Review/approval of attached phase documents}
\section{Other issues}
\begin{itemize}
\item
The group must read the compendium to know what is expected and what should be delivered.
\item
Weekly meetings are scheduled to take place at Tuesdays from 11-12. The agenda for the advisor meeting should be sent to our advisor at least the day before the meeting takes place. The agenda should containt which problems or questions the group want to discuss at the meeting.
\item
After each meeting the group must write a minutes of meeting.
\item
The group has a pre-delivery at October 14th, where some parts of the final report must be ready.
\item
The group must create a risk plan with concrete and practical solutions, a work-breakdown-structure and a project plan.
\item
The final document is really important. If the group runs out of time and some things could have been implemented better or have been omitted, this should be documented. 
\end{itemize}
\section{Next meeting}
Tuesday 2012-09-04 11:15 at ITV-464
\end{document}